%-----------EXPERIENCE-----------%
\section{\textbf {\large EXPERIENCE}}
\resumeSubHeadingListStart % chktex 1

    \resumeSubheading % chktex 1
    {Lumentum}{\emph{\textbf{January 2025 $-$ August 2025}}}
    {\textbf{System Software Solution Test Intern} $|$ \textbf{Design Verification \& Test Intern}}{Ottawa, ON}
    \resumeItemListStart % chktex 1
        \resumeItem{Developed a plugin-based Python CLI tool to parse device logs and auto-render PPTX/PDF verification reports, standardizing failure triage across engineering teams.}    
        \resumeItem{Architected an end-to-end TypeScript test automation and CI/CD pipelines to cut manual regression cycles from hours to under 30 minutes per release via GitHub Actions and Selenium/Tauri E2E.}
        \resumeItem{Automated high-risk firmware upgrades and connectivty validation across networked devices using Bash and gNOI/gNOIC, cutting engineer intervention time for routine maintenance.}
    \resumeItemListEnd % chktex 1

    \resumeSubheading % chktex 1
    {Maintenance Drone Co.}{\emph{\textbf{May 2024 $-$ December 2024}}}
    {\textbf{Software Developer Intern}}{Ottawa, ON}
    \resumeItemListStart % chktex 1
        \resumeItem{Optimized 3D point-cloud processing by implementing NumPy grid downsampling and noise filters, significantly reducing processing latency while maintaining 3D model accuracy in Blender.}
        \resumeItem{Engineered a path planning tool using the Shapely library and Matplotlib to convert KML/XML map data into optimized drone waypoint missions.}
    \resumeItemListEnd % chktex 1

    \resumeSubheading % chktex 1
    {Roof Maintenance Solutions}{\emph{\textbf{May 2022 $-$ December 2023}}}
    {\textbf{Software Developer Intern}}{Ottawa, ON}
    \resumeItemListStart % chktex 1
        \resumeItem{Streamlined data ingestion pipeline by developing Python scripts for high-volume XML annotation transfers, accelrating report generation.}
        \resumeItem{Implemented automated data validation using Regex patterns to identify and fix survey errors, eliminating costly re-inspections caused by data corruption.}
    \resumeItemListEnd % chktex 1

    

\resumeSubHeadingListEnd % chktex 1